This PDF is a Git Repo\\Containing its Own \LaTeX\ Source

### 2017-04-12 article.tex
Started making the PDF content
Background on `git bundle`

  This is a test!

>>>>

\title{This PDF is a Git Repo\\Containing its Own \LaTeX\ Source}
\author{Evan Sultanik}
\date{April 11, 2017}

\maketitle

Have you ever heard of the \texttt{git bundle} command? I hadn't. It
bundles a set of Git objects---potentially even an entire
repository---into a single file. Git allows you to treat that file as
if it were a standard Git database, so you can do things like clone a
repo directly from it. Its purpose is to easily sneakernet pushes or
even whole repositories across air gaps.
